TGI Spinal Analysis Code Experiment 2

### 2023-05-23 analysis/tgi-spinal_analysis-exp2.Rmd
results of experiment 2

## Data compiling
# trial files
setwd(datPath)
for (file in filenames){
  # trial files
  if (isTRUE(substr(basename(file), 24, 24)=="t")){
    tmp <- read.csv(file)
    tmp$ID <- substr(basename(file), 4, 6)
    tmp$manipulation <- substr(basename(file), 17, 19)
    df_trials <- rbind(df_trials, tmp)
  }
  # VAS response files
  if (isTRUE(substr(basename(file), 24, 29)=="rating")){
    tmp <- read.csv(file, header = FALSE)
    colnames(tmp) <- c('VASinit','VASburn','VASwarm','VAScold','trial_n')
    tmp$ID <- substr(basename(file), 4, 6)
    tmp$manipulation <- substr(basename(file), 17, 19)
    df_VAS <- rbind(df_VAS, tmp)
  }
  # VAS RT files
  if (isTRUE(substr(basename(file), 24, 29)=="respti")){
    tmp <- read.csv(file, header = FALSE)
    colnames(tmp) <- c('RTinit','RTburn','RTwarm','RTcold','trial_n')
    tmp$ID <- substr(basename(file), 4, 6)
    tmp$manipulation <- substr(basename(file), 17, 19)
    df_RT <- rbind(df_RT, tmp)
  }
}

# merge all files
df_res <- merge(df_trials, df_VAS, by = c('ID','trial_n','manipulation'))
df_res <- merge(df_res, df_RT, by = c('ID','trial_n','manipulation'))

@@

# incorporate demographics
# the warm and cold TGI and CNT temperatures did not code properly on the trial .csv
# have saved these in the demo .csv as well, so will add these in
demoFile <- 'STGI_participant-demographics.csv'
fileName = paste(datPath, demoFile, sep = '')
df_demo <- read.csv(fileName)
# merge
test <- merge(df_res, df_demo)

@@

# identify test results where pvalue is < .05
tgi$ID <- as.factor(tgi$ID)
i = 0
test = data.frame(matrix(nrow = 35, ncol = 3))
colnames(test) <- c('ID','pval','responder')

@@

# plotting - cold
ggplot(cold_zeff, aes(x, predicted, colour = x)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
                width = .05, size = .8) +
  labs(y = 'Predicted proportion of zeros', x = NULL) +
  ylim(0,.25) +
  scale_colour_manual(values = c(blue[4], blue[7])) +
  theme_classic() + 
  theme(legend.position = 'none',
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12)) -> plot_zcold

# warm
ggplot(warm_zeff, aes(x, predicted, colour = x)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
                width = .05, size = .8) +
  labs(y = 'Predicted proportion of zeros', x = NULL) +
  ylim(.45,.7) +
  scale_colour_manual(values = c(oran[4], oran[7])) +
  theme_classic() + 
  theme(legend.position = 'none',
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12)) -> plot_zwarm

>>>>

## Data compiling
# trial files
setwd(datPath)
for (file in filenames){
  # trial files
  if (isTRUE(substr(basename(file), 24, 24)=="t")){
    tmp <- read.csv(file)
    tmp$ID <- substr(basename(file), 4, 6)
    tmp$manipulation <- substr(basename(file), 17, 19)
    df_trials <- rbind(df_trials, tmp)
  }
  # VAS response files
  if (isTRUE(substr(basename(file), 24, 29)=="rating")){
    tmp <- read.csv(file, header = FALSE)
    colnames(tmp) <- c('VASinit','VASburn','VASwarm','VAScold','trial_n')
    tmp$ID <- substr(basename(file), 4, 6)
    tmp$manipulation <- substr(basename(file), 17, 19)
    df_VAS <- rbind(df_VAS, tmp)
  }
  # VAS RT files
  if (isTRUE(substr(basename(file), 24, 29)=="respti")){
    tmp <- read.csv(file, header = FALSE)
    colnames(tmp) <- c('RTinit','RTburn','RTwarm','RTcold','trial_n')
    tmp$ID <- substr(basename(file), 4, 6)
    tmp$manipulation <- substr(basename(file), 17, 19)
    df_RT <- rbind(df_RT, tmp)
  }
}
```

# merging
```{r data, echo = FALSE}
# merge all files
df_res <- merge(df_trials, df_VAS, by = c('ID','trial_n','manipulation'))
df_res <- merge(df_res, df_RT, by = c('ID','trial_n','manipulation'))

@@

# incorporate demographics
# the warm and cold TGI and CNT temperatures did not code properly on the trial .csv
# have saved these in the demo .csv as well, so will add these in
demoFile <- 'STGI_exp2_participant-demographics.csv'
fileName = paste(datPath, demoFile, sep = '')
df_demo <- read.csv(fileName)
# merge
test <- merge(df_res, df_demo)

@@

# identify test results where pvalue is < .05
tgi$ID <- as.factor(tgi$ID)
i = 0
test = data.frame(matrix(nrow = 40, ncol = 3))
colnames(test) <- c('ID','pval','responder')

@@

# plotting - cold
ggplot(cold_zeff, aes(x, predicted, colour = x)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
                width = .05, size = .8) +
  labs(y = 'Predicted proportion of zeros', x = NULL) +
  ylim(.20,.60) +
  scale_colour_manual(values = c(blue[4], blue[7])) +
  theme_classic() + 
  theme(legend.position = 'none',
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12)) -> plot_zcold

# warm
ggplot(warm_zeff, aes(x, predicted, colour = x)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
                width = .05, size = .8) +
  labs(y = 'Predicted proportion of zeros', x = NULL) +
  ylim(0,.25) +
  scale_colour_manual(values = c(oran[4], oran[7])) +
  theme_classic() + 
  theme(legend.position = 'none',
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12)) -> plot_zwarm
